---
title: "Simple document"
author: Fang Wang
date: 2024-9-10
output: 
   html_document: # word_document (strange!) or pdf_document
     toc: TRUE
     toc_float: TRUE
     code_folding: hide
     
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
## eval = FALSE: code will be displayed but not executed; results are not included.
## echo = FALSE: code will be executed but not displayed; results are included.
## include = FALSE: code won’t be executed or displayed.
## message = FALSE and warning = FALSE: prevents messages and warnings from being displayed.
## results = hide and fig.show = hide: prevents results and figures from being shown, respectively.
## collapse = TRUE: output will be collapsed into a single block at shown at the end of the chunk.
## error: errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it. 
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: learning assessement
 This is code for the learning assessment at P8105. 
 
```{r library, echo=FALSE, message=FALSE} 
# 
library(tidyverse)
```
I loaded necessary package "tidyverse"

```{r learning assessment}
la_df =
  tibble(
    norm_samp = rnorm(n=500, mean=1),
    samp_g0 = norm_samp >1,
    abs_v_samp = abs(norm_samp)
  )

ggplot(la_df, aes(x=abs_v_samp))+
         geom_histogram()

```
 
 
Here is code to create a histogram.
 
```{r, eval=FALSE, eco=FALSE}
ggplot(la_df, aes(x=abs_v_samp))+
         geom_histogram()
```
 
 
# Section 4: Formating text

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
 